Are you moving predictably?

### 2018-07-13 dokumentation/DecisionTree.tex
Schlaf ist nur für schwache Menschen...

\begin{figure}[H]
\centering
\begin{subfigure}{0.9\textwidth}
\includegraphics[width = \linewidth]{Dec200eqPrec.PNG}
\caption{200 in every strata}
\label{fig:decvec200}
\end{subfigure}
\begin{subfigure}{0.9\textwidth}
\includegraphics[width= \linewidth]{decvec585pre.PNG}
\caption{585 in every strata}
\label{fig:DecVec585}
\end{subfigure}
\caption{Performance for stratified person data}
\label{fig:DecVec}
\end{figure}

In \Cref{fig:DecVec} the best and worst outcome can be seen for 6 clusters. For all other configurations the outcome is similar, so just small data sets have an acceptable result and larger datasets have no sufficient results for our question.\\

>>>>

\begin{figure}[H]
\centering
\includegraphics[width = 0.9\textwidth]{Dec200eqPrec.PNG}
\caption{Performance for stratified person data with 200 in every strata}
\label{fig:decvec200}
\end{figure}

\begin{figure}[H]
\includegraphics[width= 0.9\textwidth]{decvec585pre.PNG}
\caption{Performance for stratified person data with 585 in every strata}
\label{fig:DecVec585}
\end{figure}

In \Cref{fig:DecVec200} the best and in \Cref{fig:DecVec200} theworst outcome can be seen for 6 clusters. For all other configurations the outcome is similar, so just small data sets have an acceptable result and larger datasets have no sufficient results for our question.\\

### 2018-07-13 dokumentation/MiriamClustering.tex
Schlaf ist nur für schwache Menschen...

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.69\textwidth]{vectorClustering31000.PNG}
\caption{1000 steps clustering in 3 clusters on maximal stratified person dataset}
\label{fig:1000vect3}
\end{figure}

@@

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.69\textwidth]{vectorClustering31000.PNG}
\caption{1000 steps clustering in 3 clusters on maximal stratified person dataset}
\label{fig:1000vect3}
\end{figure}

@@

As an improvent of time behaviour and as a further we apply the PCA process on the \textit{original data} without strata and a variance
threshold of 0.95. We get two Attributes, so we can assume, that the data is strongly corrleated. As expected the computating time decreases a lot for the whole process of clustering.

\begin{figure}[H]
\vspace*{-1em}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidStrata.PNG}
  \caption{Strata}
  \label{fig:PCAOrgSt}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidCluster.PNG}
  \caption{Cluster}
  \label{fig:PCAOrgCl}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{ClusterPCAOrigRapidCluster2Cluster.PNG}
  \caption{3Cluster}
  \label{fig:PCAOrgCl3}
\end{subfigure}
\caption{Distribution of original data}
\label{fig:PCAOrgDist}
\vspace*{-2em}
\end{figure}

For a clustering of 6 clusters we get a distribution, which can be seen in \Cref{fig:PCAOrgDist}, similar to the one we got from the k-means process with the same comfigurations. 
For a clustering of 3 clusters we get again results, that are not clear, visible in \Cref{fig:PCAOrgCl3}.

Using different dataset results in comparable unrewarding result.
\vspace*{-2em}

### 2018-07-13 dokumentation/theoreticalBackground.tex
Schlaf ist nur für schwache Menschen...

	The data objects within a dataset are considered to reside in a euclidean space. Thus, the euclidean distance is used to calculate a score for the similarity of two data points. When using k-Means, the quality of a cluster $C_i$ can be evaluated by computing the sum of squared errors between all data points $p$ in the object space and the centroids $c_i \in C_i$ of every cluster. This method is known as \textit{within-cluster variation} \cite{data_mining} and defined as follows: 
	\begin{equation}
		E = \sum_{i=1}^{k} \sum_{p \in C_i} dist(p, c_i)^2,
	\end{equation}
	Given $k$, the first step of k-Means is to select $k$ random points as cluster centres. Those do not have to be actual data points.
%	objects in the data set as initial representatives for the cluster centres.
	After that, each remaining data object is assigned to the best fitting cluster based on a similarity score between the data point and every cluster centre. The overall goal of k-Means clustering is to iteratively optimize the within-cluster variation. In order to achieve this, each cluster centroid is redefined as the mean of all objects within that cluster. By considering the updated centroids, every data point is reassigned to the now best fitting cluster. This iterative process will continue until no better clustering can be found.\\
%	\subsubsection{Clustering with RapidMiner}	
	As a tool we considered RapidMiner, since it has many modules already efficiently implemented and is easy to adapt.
	\vspace*{-2em}
	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=0.9\textwidth]{ClusteringRapid.PNG}
		\caption{Process of k-means clustering}
		\label{fig: kclust}
		\vspace*{-2em}
	\end{figure}

	The Process, \Cref{fig: kclust}, contains the following steps:\\
	\begin{tabular}{r c l}
		\textbf{Retrieve} & : &  gives the data into the process \\
		\textbf{Generate ID} & : & creates an ID such that we can make the comparison\\
		 & & step at the end through joining the sets\\
		\textbf{Multiply} & : & creates two identical data sets\\
		\textbf{Select Attributes} & : &  troughs away the strata before the clustering step,\\
		& & everything except cluster and id after the clustering \\
		& & and just keeps id and strata for the join step\\
		\textbf{Clustering} & : &  runs the k-means clustering algorithm. The number of \\
		& & Clusters has to be fixed \\
		\textbf{Join} & : & For comparing the clustering result and the strata we \\
		& & join the two filtered data sets by the id \\
	\end{tabular}

@@

@@

	\begin{figure}[!htbp]
		\centering
		\includegraphics[width = 0.9\textwidth]{DecisionTreeRapidModel.PNG}
		\caption{Process for decision trees in RapidMiner}
		\label{fig: RapDec}
	\end{figure}

@@

	Furthermore we choose information gain as splitting criterion (minimal gain 0.1) and a confidence of 0.25. Other configurations do not show different results.

@@

	\begin{figure}[H]
		\centering
		\includegraphics[width = 0.9\textwidth]{RapidNN.PNG}
	\end{figure}
		\begin{tabular}{r c l}
		\textbf{Retrieve} & : & includes the dataset\\
		\textbf{Replace Missing Values} & : & ensure applicable data\\
		\textbf{Discretize} & : & translates numerical to nominal data \\
		\textbf{Set Role} & : & gives strata the label role, so that the decision tree\\
		&& has those as leafs\\		
		\textbf{Cross Validation} & : & models the neural network \\
	\end{tabular}

>>>>

	The data objects within a dataset are considered to reside in a euclidean space. Thus, the euclidean distance is used to calculate a score for the similarity of two data points. When using k-Means, the quality of a cluster $C_i$ can be evaluated by computing the sum of squared errors between all data points $p$ in the object space and the centroids $c_i \in C_i$ of every cluster. This method is known as \textit{within-cluster variation} \cite{data_mining} and defined as follows: 
	\begin{equation}
		E = \sum_{i=1}^{k} \sum_{p \in C_i} dist(p, c_i)^2,
	\end{equation}
	Given $k$, the first step of k-Means is to select $k$ random points as cluster centres. Those do not have to be actual data points.
%	objects in the data set as initial representatives for the cluster centres.
	After that, each remaining data object is assigned to the best fitting cluster based on a similarity score between the data point and every cluster centre. The overall goal of k-Means clustering is to iteratively optimize the within-cluster variation. In order to achieve this, each cluster centroid is redefined as the mean of all objects within that cluster. By considering the updated centroids, every data point is reassigned to the now best fitting cluster. This iterative process will continue until no better clustering can be found.\\
%	\subsubsection{Clustering with RapidMiner}

	As a tool we considered RapidMiner, since it has many modules already efficiently implemented and is easy to adapt.

	\vspace*{-2em}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.9\textwidth]{ClusteringRapid.PNG}
		\caption{Process of k-means clustering}
		\label{fig: kclust}
		%\vspace*{-2em}
	\end{figure}

	The Process, \Cref{fig: kclust}, contains the following steps:\\

	\begin{tabular}{r c l}
		\textbf{Retrieve} & : &  gives the data into the process \\
		\textbf{Generate ID} & : & creates an ID such that we can make the comparison\\
		 & & step at the end through joining the sets\\
		\textbf{Multiply} & : & creates two identical data sets\\
		\textbf{Select Attributes} & : &  troughs away the strata before the clustering step,\\
		& & everything except cluster and id after the clustering \\
		& & and just keeps id and strata for the join step\\
		\textbf{Clustering} & : &  runs the k-means clustering algorithm. The number of \\
		& & Clusters has to be fixed \\
		\textbf{Join} & : & For comparing the clustering result and the strata we \\
		& & join the two filtered data sets by the id \\
	\end{tabular}

@@

\subsubsection{Principal component analysis}

\textit{PCA} uses an orthogonal transformation to convert a dataset with correlated datas into a dataset without correlations and decreased dimension. This is a helpful technique to have a better understanding of the data complexity as well as an improvment of time consumption in further steps.

The first component for the PCA transformation has to satisfy the following:

\vspace*{-1em}
\begin{align*}
w_1 &= \text{argmax}_{||w|| = 1} \{\sum_i (t_1)_i^2\}\\
	&= \text{argmax}_{||w|| = 1} \{\sum_i (x_iw)^2\}
	\vspace*{-2em}
\end{align*}

Which is achieved by the corresponding eigenvector.

The next components need to fullfill:
\begin{align*}
\hat{X}_k &= X - \sum_{s=1}^{k-1} Xw_sw_s^T\\
w_k &= \text{argmax}_{||w|| = 1} \{||\hat{X}_kw||^2\}\\
	&= \text{argmax}_{||w|| = 1} \{\frac{w^T\hat{X}_k^T\hat{X}_kw}{w^Tw}\}
	\vspace*{-1em}
\end{align*}

Based on the 'weight matrix' a mapping is possible from the original space to a new space in which the dataset is uncorrelated.

	\vspace*{-1em}
	\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\textwidth]{PCAClustering}
	\caption{RapidMiner process for PCA and k-means}
	\label{fig:PCA}
	\vspace*{-2em}
	\end{figure}

The Process does the following steps, like in \Cref{fig:PCA} visible:

\begin{tabular}{r c l}
	\textbf{Retrieve} & : & gives the data in the process.\\
	\textbf{Generate Id} & : & creates an idea for the join later\\
	\textbf{Select Attribute} & : & just gives the chosen attributes back\\
	\textbf{Nominal to Numerical} & : & changes the nominal data to numerical data, so \\
	&&that we can apply PCA in the next step \\
	\textbf{PCA} & : & applys the PCA reduction to the data\\
	&& threshold $0.95$ \\
	\textbf{Clustering} & : &  clusters the given data \\
	\textbf{Join} & : & joins the clustering outcome and the strata by the\\
	&& ID\\
\end{tabular}

@@

	\vspace*{-2em}
	\begin{figure}[H]
		\centering
		\includegraphics[width = 0.9\textwidth]{DecisionTreeRapidModel.PNG}
		\caption{Process for decision trees in RapidMiner}
		\label{fig: RapDec}
		\vspace*{-1.5em}
	\end{figure}

@@

	Furthermore we choose information gain as splitting criterion (minimal gain 0.1) and a confidence of 0.25. Other configurations do not show different results.
	\vspace*{-1em}

@@

	\vspace*{-2em}
	\begin{figure}[H]
		\centering
		\includegraphics[width = 0.9\textwidth]{RapidNN.PNG}
		\caption{RapidMiner process for neural nets}
		\vspace*{-1em}
	\end{figure}

	\begin{tabular}{r c l}
		\textbf{Retrieve} & : & includes the dataset\\
		\textbf{Replace Missing Values} & : & ensure applicable data\\
		\textbf{Discretize} & : & translates numerical to nominal data \\
		\textbf{Set Role} & : & gives strata the label role, so that the decision tree\\
		&& has those as leafs\\		
		\textbf{Cross Validation} & : & models the neural network \\
	\end{tabular}
